The Impact of Cloud Computing in $10$ Years

### 2013-05-04 essay/tex/essay.tex
write education part one.

\section{Introduction}
In recent years, cloud computing has provided us with a lot of benefits in many area. Major cloud computing vendors like Amazon, Google and Dropbox have offered the users around the world a cheap, convenient and secure computing and storage resource. For example, Amazon EC2 is one of the most popular cloud computing platform for many companies and individuals. The various types of virtual instances at different price strategies provide very flexible choices for the users. I rent a \emph{m1.micro} instance for the use of my person website and blog for three years at a decent price around $100$ dollas. With the virtual instance, I do not need to install a physical machine at my home and maintain it day by day, which definitely costs more than $100$ dollas for three years.

An additional example of another scenario of cloud computing's application could be cloud storage. Either Dropbox or Google Drive or Amazon Cloud Storage, they provide both companies and individuals cheap and convenient cloud storage which we do not need to worry about the data loss or accessibility. Even though three of them have different data privacy terms, people still quite enjoy this type of services. For example, Dropbox has a marketing plan for university students who has a \emph{.edu} email will obtain an extra $3$GB plus his own $2$GB storage space for free. When I look around with other students, most of them seems to be very happy with the current services. They use Dropbox as a USB drive to share or transfer large amount of data over the air; they also use Dropbox to show pictures or documents during their presentation. Thus, it seeems that the free $5$GB \emph{USB-air-drive} could become more popular and convenient than a $\$10$-$\$15$ USB flash drive.

@@

\section{Massive Open Online Courses and Cloud Computing}

@@

\section{Online-to-Offline Market and Cloud Computing}

>>>>

\section{Introduction}
In recent years, cloud computing has provided us with a lot of benefits in many area. Major cloud computing vendors like Amazon, Google and Dropbox have offered the users around the world a cheap, convenient and secure computing and storage resource. For example, Amazon EC2 is one of the most popular cloud computing platform for many companies and individuals. The various types of virtual instances at different price strategies provide very flexible choices for the users. I rent a \emph{m1.micro} instance for the use of my person website and blog for three years at a decent price around $100$ dollas. With the virtual instance, I do not need to install a physical machine at my home and maintain it day by day, which definitely costs more than $100$ dollas for three years. Besides individual users like me, many companies either big ones like Netflix or startups like Pinterest choose Amazon AWS as their dedicated IT infrastructure to reduce the cost of maintaining a complete IT infrastructure by themselves.

An additional example of another scenario of cloud computing's application could be cloud storage. Either Dropbox or Google Drive or Amazon Cloud Storage, they provide both companies and individuals cheap and convenient cloud storage which we do not need to worry about the data loss or accessibility. Even though three of them have different data privacy terms, people still quite enjoy this type of services. For example, Dropbox has a marketing plan for university students who has a \emph{.edu} email will obtain an extra $3$GB plus his own $2$GB storage space for free. When I look around with other students, most of them seems to be very happy with the current services. They use Dropbox as a USB drive to share or transfer large amount of data over the air; they also use Dropbox to show pictures or documents during their presentation. Thus, it seeems that the free $5$GB \emph{USB-air-drive} (which I called for Dropbox) could become more popular and convenient than a $\$10$-$\$15$ USB flash drive.

Event if cloud computing had achieved so many advantages all over these years, we may notice that the current stage of cloud computing has influenced very limited industries, most of them are concentrated in Internet or Web related businesses. Two major use of the cloud infrastructure are application host and storage service. However, the

@@

\section{Education and Cloud Computing}
At the current stage, cloud computing seems to have little interactions with education field, especially the primary and secondary educations. Perhaps the email system could be the only possible connections for the public schools and cloud computing, although not all the public school system will use a cloud email services from Google or Microsoft. My wife is a substitute teacher in Knox county school and she was a substitute teacher in Webb School at Knoxville as well. She tells me there is a big difference of the education philosophy and approach between Knox county school and Webb school. For Webb school at Knoxville, teaching has been computerized. The teachers prepare their course material with iPad or laptop, and every student uses an iPad in class for reading, interactions and homeworks. There is no physical textbooks really necessary in my wife's teaching at Webb school.

In addition to the course material, Webb school has a strong IT team to support the teachers and students. At the new teacher training, the IT stuff at Webb school provides numerous apps inside the Apple store which could potentially benefits their teaching. For example, the students usually finish their homework on iPad and submit the assignment through an app, the teacher can grade it and analyze the performance of the student from its history. One thing I am impressed by this school is that the IT team did not create their own infrastructure in school. However, they use cloud computing as their complete IT infrastructure. For instance, the email system is provided by Google; the reading assignment system is provided by GoodReader, an impressive reading experience provider on mobile devices; student uses eBagpack as an educational Dropbox to management their study materials; and they use edmodo as a educational social network for student to vote and for teacher to post updates about the course.

At present, very few schools like Webb school have the opportunity to use cloud computing to support both the school daily management and teachings/learnings. Let us take the Knox county school as an example. The school management system  and other IT infrastructure is maintained by the school's IT team. Perhaps it is a reliable system, but it definitely cost more than using a cloud vendor's product. On the other hand, the students in the public school still use textbook to learn and the teachers handle the teachings, assignments and homework traditionally. One of my friends, he teaches fourth grade at Knox county school. He is not satisfied with the current system he has in class, even though he already uses Smartboard (a computerized white board) to teach. He hopes to have a better tool to keep track of the student's performance throughout these years instead of using Excel. He thinks the cost may be one of the major reason for the school to decide build a new system.

Note that the difference between independent schools and public school is not to show how well the independent school is, but to illustrate the trend of cloud computing and education which the cloud computing can help improve the education strategy.

On one hand, more and more schools realize the importance of IT infrastructure in class. We need to teach the students how to organize the information well at the beginning. An easy way to start with is to teach them how to use electronic materials and make them familiar with this learning style. From this point of view, the schools need a new system to adapt the changes and needs, but the cost is non-trivial if every school builds their own.

On the other hand, fortunately, many startups have started to build such a system under the schools' needs. Each individual product can be used by different schools and students that all of them actually share the same system. The products like eBackpack or edmodo are almost free to everyone to use or small amount of fee is charged, which definitely can reduce the cost for the schools to replace the old system. Besides, the cloud computing vendors can provide those startups many advantages, such as agile development and deployment, low computation and storage cost and almost zero IT maintenance cost, so that the product vendors can run their service or product at their lowest cost.

In addition to the lower level education system, the cloud computing also benefits the higher education system.

\section{Online-to-Offline Business and Cloud Computing}

@@
